\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables

%\usepackage{arev}
\usepackage{listings}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{rotating}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{color}
\usepackage{tikz}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[noend]{algpseudocode}
\usepackage{algorithm,float}
\usepackage{array}
\usepackage{enumitem}
\usetikzlibrary {shapes.geometric,positioning,arrows,shadows}
\usetikzlibrary{decorations.pathreplacing}
\definecolor{myBlue}{RGB}{0,162,227}
\definecolor{apricot}{RGB}{251,185,130}
\renewcommand{\theoremautorefname}{Definition}


 
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}

\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}


% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}



% DOI
%\acmDOI{10.475/123_4}

% ISBN
%\acmISBN{123-4567-24-567/08/06}

%Conference
%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
%  Paso, Texas USA} 
%\acmYear{1997}
%\copyrightyear{2016}
%
%\acmPrice{15.00}

%\title: Think Outside the Box: Exploring and Exploiting Cross-Language Optimizations in SCOPE
\newcommand{\nonNativeTimeL}{43.70}
\newcommand{\nonNativeTimeU}{73.32}
\newcommand{\optimizableU}{0.16}
\newcommand{\potentiallyOptimizableU}{6.76}
\newcommand{\potentiallyOptimizableL}{1.01}




\begin{document}
\title{Cross-Language Optimizations in Big Data Systems: A Case Study of SCOPE}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}


\author{Marija Selakovic}

%\orcid{1234-5678-9012}
\affiliation{%
  \institution{TU Darmstadt}
  \state{Germany} 
}
\email{m.selakovic89@gmail.com}

\author{Michael Barnett, Madan Musuvathi, Todd Mytkowicz}

\affiliation{%
  \institution{Microsoft Research}
  \state{USA} 
}
\email{mbarnett, madanm, toddm@microsoft.com}

%\author{Madan Musuvathi}

%\affiliation{%
%  \institution{Microsoft Research}
%    \state{USA} 
%    }

  
%\email{madanm@microsoft.com}



%\author{Todd Mytkowicz}

%\affiliation{%
%  \institution{Microsoft Research}
%    \state{USA} 
%    }

  
%\email{toddm@microsoft.com}


% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{M. Selakovic et al.}


\begin{abstract}

  Building scalable big data programs currently requires programmers to combine relational (SQL) with non-relational code (Java, C\#, Scala).
  Relational code is declarative --- a program describes \emph{what} the computation is and the compiler decides \emph{how} how to distribute the program.  SQL query optimization has enjoyed a rich and fruitful history, however, most research and commercial optimization engines treat non-relational code as a black-box and thus are unable to optimize it.

  This paper empirically studies over 3 million SCOPE programs across five data centers within Microsoft and finds programs with non-relational code take between 45-70\% of data center CPU time.
  We further explore the potential for SCOPE optimization by generating more native code from the non-relational part. Finally, we present 5 case studies showing that triggering more generation of native code in these jobs yields significant performance improvement: optimizing just one portion resulted in as much as 25\% improvement for an entire program.

\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%



%\keywords{ACM proceedings, \LaTeX, text tagging}


\maketitle

\input{sections/introduction}
\input{sections/background}
\input{sections/profiingInfrastructure}
\input{sections/evaluation}
\input{sections/caseStudies}
\input{sections/limitations}
\input{sections/relatedWork}
\input{sections/future}
\input{sections/conclusions}

\section*{Acknowledgements}
We want to especially thank the SCOPE team for answering our endless questions and also the product groups that helped us experiment with their scripts.

\bibliographystyle{ACM-Reference-Format}
\bibliography{references} 

\end{document}
